rbeast2: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-19 article.tex
Removed 'create_', thanks @rsetienne, Hadley Wickham, Hanno Hildenbrandt

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  site_models = create_hky_site_model(),
  clock_models = create_rln_clock_model(),
  tree_priors = create_bd_tree_prior()
)
\end{lstlisting}

@@

\begin{table}[]
\centering
\begin{tabular}{ | l | l | }
\hline
\textbf{Name} & \textbf{Description} \\
\hline
\verb;create_beast2_input_file; & Creates a BEAST2 input file \\
\hline
\verb;create_gtr_site_model; & Create a GTR site model \\
\verb;create_hky_site_model; & Create an HKY site model \\
\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
\verb;create_tn93_site_model; & Create a TN93 site model \\
\hline
\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
\verb;create_strict_clock_model; & Create a strict clock model \\
\hline
\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
\verb;create_yule_tree_prior; & Create a Yule tree prior \\
\hline
\verb;create_beta_distr; & Create a beta distribution \\
\verb;create_exp_distr; & Create an exponential distribution \\
\verb;create_gamma_distr; & Create a gamma distribution \\
\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
\verb;create_laplace_distr; & Create a Laplace distribution \\
\verb;create_log_normal_distr; & Create a log-normal distribution \\
\verb;create_normal_distr; & Create a normal distribution \\
\verb;create_one_div_x_distr; & Create a 1/X distribution \\
\verb;create_poisson_distr; & Create a Poisson distribution \\
\verb;create_uniform_distr; & Create a uniform distribution \\
\hline
\end{tabular}
\caption{rbeast2's main functions}
\label{tab:functions}
\end{table}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  c("anthus_aco.fas", "anthus_nd2.fas"),
  site_models = list(
    create_tn93_site_model(), 
    create_gtr_site_model()
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  tree_priors = create_yule_tree_prior(
    birth_rate_distr = create_exp_distr()    
  )
)
\end{lstlisting}

>>>>

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  site_models = hky_site_model(),
  clock_models = rln_clock_model(),
  tree_priors = bd_tree_prior()
)
\end{lstlisting}

@@

\begin{table}[]
\centering
\begin{tabular}{ | l | l | }
\hline
\textbf{Name} & \textbf{Description} \\
\hline
\verb;create_beast2_input_file; & Creates a BEAST2 input file \\
\hline
\verb;gtr_site_model; & Create a GTR site model \\
\verb;hky_site_model; & Create an HKY site model \\
\verb;jc69_site_model; & Create a Jukes-Cantor site model \\
\verb;tn93_site_model; & Create a TN93 site model \\
\hline
\verb;rln_clock_model; & Create a relaxed log-normal clock model \\
\verb;strict_clock_model; & Create a strict clock model \\
\hline
\verb;bd_tree_prior; & Create a birth-death tree prior \\
\verb;cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
\verb;ccp_tree_prior; & Create a coalescent constant-population tree prior \\
\verb;cep_tree_prior; & Create a coalescent exponential-population tree prior \\
\verb;yule_tree_prior; & Create a Yule tree prior \\
\hline
\verb;beta_distr; & Create a beta distribution \\
\verb;exp_distr; & Create an exponential distribution \\
\verb;gamma_distr; & Create a gamma distribution \\
\verb;inv_gamma_distr; & Create an inverse gamma distribution \\
\verb;laplace_distr; & Create a Laplace distribution \\
\verb;log_normal_distr; & Create a log-normal distribution \\
\verb;normal_distr; & Create a normal distribution \\
\verb;one_div_x_distr; & Create a 1/X distribution \\
\verb;poisson_distr; & Create a Poisson distribution \\
\verb;uniform_distr; & Create a uniform distribution \\
\hline
\end{tabular}
\caption{rbeast2's main functions}
\label{tab:functions}
\end{table}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  c("anthus_aco.fas", "anthus_nd2.fas"),
  site_models = list(
    tn93_site_model(), 
    gtr_site_model()
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  tree_priors = yule_tree_prior(
    birth_rate_distr = exp_distr()    
  )
)
\end{lstlisting}
